TacticToe: Learning the Game of Tactics

### 2018-02-19 tactictoe_jv.tex
Minor

\section{Prediction}\label{s:prediction}
The learning-based selection of relevant lemmas significantly improves the
automation for hammers~\cite{BlanchetteGKKU16}. In \tactictoe, we use the
distance-weighted \emph{$k$ nearest-neighbour} classifier~\cite{DudaniS76}
adapted for lemma selection~\cite{ckju-pxtp13}. It allows for hundreds of
predictions per second, while maintaining very high prediction quality~\cite{femalecop}.
We rely on this supervised machine learning algorithm to predict three 
different kinds of objects:
 tactics, theorems and lists of goals. The number of predicted objects $k$ is
 called the \emph{prediction radius}. For a goal $g$, we note
$\mathit{Predictions}^{\mathit{tactic}}_k (g)$ (respectively
$\mathit{Predictions}^{\mathit{theorem}}_k (g)$
and $\mathit{Predictions}^{\mathit{goal\_list}}_k (g)$) the $k$ tactics 
(respectively theorems and lists of goals) selected by our prediction algorithm.

@@

\section{Abstraction}\label{sec:synthesis}
One of the great weakness of the previous version of \tactictoe is that
it could not create its own tactics. Indeed, sometimes no previous tactic is
adapted for a certain goal and creating a new tactic is necessary.
%Experiments in section, show how different degrees of tactic synthesis could
%improve the success rate of \tactictoe.
We present a way to create tactics with different arguments
by abstracting them and re-instantiating them using a predictor for that kind
of argument. In the spirit of the orthogonalization method, we will try to
create tactics that are more general but have the same effect as the
ungeneralized one. The generalized tactics are typically slower that their 
counterpart, but the added flexibility is worthwhile in practice. Moreover, 
since we impose a timeout on each tactic (0.05 seconds by default), very slow 
tactics fails and thus are not selected.

>>>>

\section{Prediction}\label{s:prediction}
The learning-based selection of relevant lemmas significantly improves the
automation for hammers~\cite{BlanchetteGKKU16}. In \tactictoe we use the
distance-weighted \emph{$k$ nearest-neighbour} classifier~\cite{DudaniS76}
adapted for lemma selection~\cite{ckju-pxtp13}. It allows for hundreds of
predictions per second, while maintaining very high prediction quality~\cite{femalecop}.
We rely on this supervised machine learning algorithm to predict three 
different kinds of objects:
 tactics, theorems and lists of goals. The number of predicted objects $k$ is
 called the \emph{prediction radius}. For a goal $g$, we note
$\mathit{Predictions}^{\mathit{tactic}}_k (g)$ (respectively
$\mathit{Predictions}^{\mathit{theorem}}_k (g)$
and $\mathit{Predictions}^{\mathit{goal\_list}}_k (g)$) the $k$ tactics 
(respectively theorems and lists of goals) selected by our prediction algorithm.

@@

\section{Abstraction}\label{sec:synthesis}
One of the major weakness of the previous version of \tactictoe is that
it could not create its own tactics. Indeed, sometimes no previous tactic is
adapted for a certain goal and creating a new tactic is necessary.
%Experiments in section, show how different degrees of tactic synthesis could
%improve the success rate of \tactictoe.
We present a way to create tactics with different arguments
by abstracting them and re-instantiating them using a predictor for that kind
of argument. In the spirit of the orthogonalization method, we will try to
create tactics that are more general but have the same effect as the
ungeneralized one. The generalized tactics are typically slower that their 
counterpart, but the added flexibility is worthwhile in practice. Moreover, 
since we impose a timeout on each tactic (0.05 seconds by default), very slow 
tactics fails and thus are not selected.
